\Large \bf On semidefinite-representable sets over valued fields

### 2025-10-06 article/paper_padic_spec.tex
commit by Simone

\usepackage{geometry}
\geometry{
 a4paper,
 %total={170mm,257mm},
 left=30mm,
 right=30mm,
 top=30mm,
 bottom=30mm
}

@@

\begin{definition}
  \label{def_polyhedra}
  A \emph{polyhedron} is a subset $P \subset K^n$ of the form
  $$
  P = \{x \in K^n : \val(\ell_i(x)) \geq 0, i=1,\ldots,d \text{ and }
  \val(m_j(x)) = +\infty, j=1,\ldots,e\},
  $$
  for some $\ell_1,\ldots,\ell_d,m_1,\ldots,m_e \in K[x]_1$.
\end{definition}

@@

\begin{theorem}[DI] 
Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron of $K^n.$
Then $f(\PP)$ is a polyhedron. \label{theo:DI}
\end{theorem}

We prove the result by reducing to particular cases.
The strategy to deduce the main theorem DI 
is the following:
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[
  node distance=1cm and 1cm,
  box/.style={draw, rounded corners, minimum width=2.2cm, minimum height=1cm, align=center},
  thickarrow/.style={->, >=Stealth, line width=1.2pt},
]

% Nodes
\node[box] (DIdiag) {DI${}_{diag}$};
\node[box, right=of DIdiag] (DIproj) {DI${}_{proj}$};
\node[box, right=of DIproj] (DIl) {DI${}_{l}$};
\node[box, right=of DIl] (DIi) {DI${}_{i}$};
\node[box, right=of DIi] (DI) {DI};

\node[box, above=of DIproj] (DIimm) {DI${}_{imm}$};
\node[box, below=of DIproj] (DIaut) {DI${}_{aut}$};

% Arrows
\draw[thickarrow] (DIdiag) -- (DIproj);
\draw[thickarrow] (DIproj) -- (DIl);
\draw[thickarrow] (DIl) -- (DIi);
\draw[thickarrow] (DIi) -- (DI);

\draw[thickarrow] (DIimm) -- (DIl);
\draw[thickarrow] (DIaut) -- (DIl);

\end{tikzpicture}
\caption{Strategy of proof of Theorem \ref{theo:DI}.}
\label{fig:di-properties}
\end{figure}

We begin by the cases of linear maps in $GL_n(O_K)$.

\begin{lemma}[DI${}_{aut}$]
Let $f \in GL_n(O_K)$ and $\PP$ a polyhedron of $K^n$.
Then $f(\PP)$ is a polyhedron. \label{lem:DIaut}
If in addition, $\PP$ is defined only by inequalities,
then so is $f(\PP)$.
\end{lemma}
\begin{proof}
If $\PP$ is defined (in matrix form) by \[\left\lbrace X \in K^n,  AX+B \geq 0, CX+D=0 \right\rbrace\] and $U$ is the matrix of $f$ in the canonical basis of $K^n$, 
let $\Qc$ be defined by \[\left\lbrace Y \in K^n,  AU^{-1} Y+B \geq 0, CU^{-1} Y+D=0 \right\rbrace.\]
Then it is clear that $\Qc$ is a polyhedron and $f(\PP)=\Qc.$
It is also clear that if $\PP$ is defined only by inequalities,
then so is $f(\PP)$.
\end{proof}

@@

\begin{lemma}[DI${}_{diag}$]
Let $f : K^n \to K^n$ be a linear map and $\PP$ a polyhedron of $K^n$ defined only by inequalities. We assume that the matrix of $f$ in the canonical basis of $K^n$ is diagonal.
Then $f(\PP)$ is a polyhedron. \label{lem:DIdiag}
\end{lemma}
\begin{proof}
As in the proof of Lemma \ref{lem:DIaut} DI${}_{aut}$, a trivial change
of variables is enough to conclude.
\end{proof}

@@

\begin{lemma}[DI${}_{proj}$]
Let $f : K^n \to K^n, \: (x_1,\dots,x_{n-1},x_n) \mapsto (x_1,\dots,x_{n-1})$ and $\PP$ a polyhedron of $K^n$ defined only by inequalities. 
Then $f(\PP)$ is a polyhedron defined only by inequalities. \label{lem:DIproj}
\end{lemma}
\begin{proof}
We assume that $\PP \neq \emptyset$.
Let us write the conditions defining $\PP$
in matrix form:
$\val(A X+B) \geq 0$ 
with $A \in M_{q,n}(K)$, $B \in K^q$
and $X=(x_1,\dots,x_n)^\intercal$.

@@

\begin{lemma}[DI${}_{imm}$]
Let $f : K^l \to K^n$ be the immersion $(x_1,\dots, x_l) \mapsto (x_1,\dots, x_l,0,\dots, 0)$ and $\PP$ a polyhedron of $K^l$
Then $f(\PP)$ is a polyhedron. \label{lem:DIimm}
\end{lemma}
\begin{proof}
Adding the equalities $x_{l+1}=0, \dots, x_n=0$ to the equations and inequations in
$x_1,\dots, x_l$ defining $\PP$, the result is clear.
\end{proof}

@@

\begin{proposition}[DI${}_l$]
Let $f : K^n \to K^m$ be a linear map and $\PP$ a polyhedron of $K^n$ defined only by inequalities.
Then $f(\PP)$ is a polyhedron. \label{prop:DIl}
\end{proposition}
\begin{proof}
We assume that $\PP \neq \emptyset$, and we identify $f$ with its matrix in $\allmat_{n,m}(K)$.
We assume that $\PP$ is defined as $\left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I\right\rbrace$ for some
finite sets $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .

@@

We can generalize from linear mappings to affine mappings.
\begin{proposition}[DI${}_i$]
Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron of $K^n$ defined only by inequalities.
Then $f(\PP)$ is a polyhedron. \label{prop:DIi}
\end{proposition}
\begin{proof}
Let $P \in K^m$. One can see by immediate change of variables that $\Qc$ is a polyhedron of $K^m$ if and only if
$\Qc+P$ is a polyhedron of $K^m$.
Consequently, translating by $-f(O)$ in the codomain, one can reduce
to the case of Proposition \ref{prop:DIl}   DI${}_l$.
\end{proof}

@@

\begin{proof}[Proof of Theorem \ref{theo:DI} DI]
Here, $f : K^n \to K^m$ is an affine map and $\PP$ a polyhedron of $K^n.$
Let us write $\PP = \PP_I \cap \PP_E$
with $\PP_I := \left\lbrace X \in K^n,  AX+B \geq 0 \right\rbrace$
and $\PP_E := \left\lbrace X \in K^n,  CX+D=0 \right\rbrace = P + \overrightarrow{\PP_E}.$ 
Then $f(\PP) = f_{\PP_E}(\PP_I).$

By a translation of $-P$ in $K^n$, we can assume that
$\PP_E$ is a linear vector space: we are reduced to proving that, if $\tilde{f}: \PP_E \to K^m$ is an affine map and $\PP_I$ is a polyhedron of the vector space $\PP_E$ defined only by inequalities, then  $\tilde{f}(\PP_I)$ is a polyhedron.
This is the case thanks to Proposition \ref{prop:DIi} DI$_i$
and the theorem is proven.
\end{proof}

@@

\begin{proposition}[Characterization of polyhedra] \label{prop:carac}
    Polyhedra are either empty or the image of polydiscs under a linear mapping.
\end{proposition}
\begin{proof}
    Let $\mathcal{P}$ be a polyhedron in $K^n$. Then $\mathcal{P} = \{x \in K^n : Ax+B \ge 0, Dx = e\}$ for some $A \in K^{d \times n}, b \in K ^d,  D\in  K^{m\times n}, e \in K^m$.

    If $\mathcal{P}$ is nonempty then there exists $x_0 \in K^n$ such that $Dx_0=e$. Let $J \in K^{n \times R}$ such that $\textrm{Im} J = \ker D$ where $R$ denotes the dimension of $\ker D$. Then $\mathcal{P} = x_0 + J\mathcal{P}'$ where $A' := AJ$ $b' := Ax_0 + b$ and  $\mathcal{P'} := \{y \in K ^R: A'y + b' \ge 0 \}$.

    Now let $S \in K^{n\times R}$ be the SNF of $A'$ and $Q \in \GL_n\left(\mathcal{O}_K\right)$ and $P \in \GL_R\left(\mathcal{O}_K\right)$ such that $A'= Q S P^{-1}$.
    Then $\mathcal{P'} = \{y \in K^R : QSP^{-1}y + b' \ge  0\} = P\{z \in K^R : Sz + Q^{-1}b' \ge 0 \}$.
    Let $b'':=Q^{-1}b$ then $P' = P \{z \in K^R : s_i z_i + b''_i \ge 0, i= 1\ldots R\}$. The set $\{z \in K^R : s_i z_i + b_i \ge 0\}$ is either empty or a polydisc (with eventually infinite radii) and $\mathcal{P} = x_0 + JP \{z \in K^R: s_i z_i + b_i \ge  0, i=1,\ldots,R\}$ which concludes the proof.

@@

\begin{corollary} \label{cor:caracdim1}
   If $\mathcal{P}$ is a polyhedron in $K$ then $\mathcal{P}$ is either empty or a ball (eventually with infinite radius).
\end{corollary}

\begin{proof}
    Let $\mathcal{P}$ be such polyhedron. We assume that $\mathcal{P} \neq \emptyset$. By \ref{prop:carac} there exist a polydisc $D = \{x \in K^n : \val s_i x_i - b_i \ge 0, i=1,\ldots,n \}$ for some $s_1,\ldots,s_n, b_1,\ldots,b_n \in K ^n$ and an affine map $f : K^n \to K$ such that $\mathcal{P} = f(D)$. Let $a_0,a_1,\ldots,a_n \in K$ such that $f(x) = a_0 + a_1 x_1 + \ldots + a_n x_n$. We can assume, with no loss of generality, that the $a_i$'s are nonzero.

If there exists $i_0 \in \{1,\ldots,n\}$ such that $s_{i_0} = 0$ then $\mathcal{P} = f(D) = K$ and $\mathcal{P}$ is a ball of infinite radius. Otherwise, we have $D = \{x \in K^n : x_i = \frac{b_i}{s_i} + O\left( \pi^{-val s_i} \right), i=1,\ldots,n \}$ and therefore for all $x \in  K$, $x \in P$ if and only if $x = a_0 + \sum_{i=1}^{n}( \frac{a_i b_i}{s_i} + O\left( \pi^{\val a_i - \val s_i} \right))= a_0  + \sum_{i=1}^{n} \frac{a_i b_i}{s_i} + O(\pi^d)$ where $d = \min \limits_{i = 1,\ldots,n} \val a_i - \val s_i$. Thus $\mathcal{P} = \{x \in K : \val (x - a_0 - \sum_{i=1}^{n} \frac{a_i b_i}{s_i}) \ge d \}$ is a ball.

@@

A \emph{linear programming problem} (or \emph{linear program}) \emph{with data $(A,b,c,D,e)$} is defined
as:
\begin{equation}
  \tag{LP}\label{LP}
\begin{array}{rcll}
  p^* & := & \inf_{x \in K^n} & \val \left\langle c, x \right\rangle \\
  &    & \text{s.t.}         & A x + b \geq 0\\
  & & & D x = e
\end{array}
\end{equation}
with $c \in K^n$ a fixed vector of size $n$ that represents the cost,
$A \in K^{d \times n}$, $b \in K^d$, $D \in K^{m\times n}$, $e \in K^m$ 
and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$.
When $A$ is a diagonal matrix,
we refer to \eqref{LP} as a \emph{diagonal} linear program.
We denote the \emph{feasible set} of \eqref{LP} by
\begin{equation*}
\begin{aligned}
  \PP  &= \{x \in K^n : Ax + b \geq 0, Dx = e\}.
\end{aligned}
\end{equation*}
A vector $x \in K^n$ is called \emph{feasible} for~\eqref{LP} if $x \in \PP$. A feasible vector $x^* \in \PP$ is called a \emph{solution} to \eqref{LP} if $p^* = \val\left\langle c,x^*\right\rangle$, namely, if the infimum in \eqref{LP} is attained at $x^*$.

@@

\begin{lemma}\label{solutions}
  Let $(S,b',c',{\bf 0}, 0)$ be as in \Cref{solsLP} and assume \eqref{LP} is feasible.
  %%%$\PP' \neq \emptyset$.
  %%%= \{y \in K^n : Sy+b' \geq 0\}
  For $\lambda = -\sum_{i=1}^r c'_i b'_i/s_i$ and $v = \min_{1\le i\le r} \val (c'_i/s_i)$,
  one has:
  \begin{enumerate}
  \item
    if $\val \lambda < v$, the minimum is $\val \lambda$ and is attained on the whole feasible
    set; \label{solutions:it1}
  \item
    if $\val \lambda \geq v$, the minimum is $v$ and is attained on
    ${\bf e}_j \in K^n$, the vector with all $0$'s except with a $1$ on the $j$-th component,
    with $j$ satisfying $\val (c'_j/s_j) = v$. \label{solutions:it2}
  \end{enumerate}
  %One has
  %$$
  %\langle c',\mathcal{P}'\rangle = \lambda + \pi^v\OK.
  %$$
  %If attained on every $x \in \mathcal{P}'$;
\end{lemma}
\begin{proof}
  The feasible set $\PP' = \{y \in K^n : Sy+b' \geq 0\}$ of the diagonal LP can be written
  as the set of vectors $y \in K^n$ that verifies $s_i y_i + b'_i \in \OK$ for $i=1,...,r$.
  In other words:
  $$
  \PP' = \left\{\left[\begin{smallmatrix} y_1\\ \vdots\\ y_n \end{smallmatrix}\right] \in K^n :
  y_i \in -\frac{b'_i}{s_i} + \frac{1}{s_i} \OK, 1\le i\le r\right\}.
  $$
  The minimum in \eqref{LP} is the minimum of
  $y \mapsto \val\left(\left\langle c',y \right\rangle\right)$ on $\PP'$.
  The image of $\PP'$ by $y \mapsto \left\langle c',y \right\rangle$ is
  \[
  \left\langle c',\PP' \right\rangle = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right) = \lambda + \pi^{v} \OK.
  \]
  Two cases can occur depending on $v$ and the valuation of $\lambda$.
  If $\val(\lambda) < v$, the minimum of $y\mapsto \val\left(\left\langle c',y \right\rangle\right)$ over $\PP'$ is reached at any point of $\PP'$, and is equal to $\val(\lambda)$.
  Otherwise, $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$ of $\PP'$ such that
  $\left<c',y \right> \in \pi^v\OK$.
\end{proof}

@@

Recall that the \emph{Newton polygon} of a polynomial $P = \sum_{i=0}^{d} a_i T^i \in K[T]$ is
defined as the inferior convex hull of the set $\{(i, \val a_i) \,|\, 0 \le i \le d\}$, {\it i.e.} the
graph of the greatest convex function $\mathcal{P} : [0,d] \to \R$ such that $\mathcal{P}(i) \leq \val a_i$
for $i=1,\ldots,d$. This function is piecewise affine and its slopes are exactly the opposites of the valuations
of the roots of $P$.

@@

\begin{definition}
  A subset $S$ of $K^n$ is said \emph{semialgebraic} if it is defined by finite unions and intersections of sets defined by polynomial equalities of the form $\{ x \in K^n  : P( x) = 0 \}$ and of sets defined by polynomial inequalities of the form $\{ x\in K^n : \val P(x) \geq 0 \}$.
\end{definition}

>>>>

\usepackage{geometry}
\geometry{
 a4paper,
 %total={170mm,257mm},
 left=33mm,
 right=33mm,
 top=35mm,
 bottom=35mm
}

@@

\begin{definition}
  \label{def_polyhedra}
  A \emph{polyhedron} is a subset $\PP \subset K^n$ of the form
  $$
  \PP = \{x \in K^n : \val(\ell_i(x)) \geq 0, i=1,\ldots,d \text{ and }
  \val(m_j(x)) = +\infty, j=1,\ldots,e\},
  $$
  for some $\ell_1,\ldots,\ell_d,m_1,\ldots,m_e \in K[x]_1$.
\end{definition}

@@

\begin{theorem}[DI] 
Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron in $K^n.$
Then $f(\PP)$ is a polyhedron. \label{theo:DI}
\end{theorem}

We prove the result by reducing to particular cases.
The strategy to deduce the main theorem DI 
is given in \Cref{fig:di-properties}.

\begin{figure}[!ht] 
\centering
\begin{tikzpicture}[
  node distance=1cm and 1cm,
  box/.style={draw, rounded corners, minimum width=2.2cm, minimum height=1cm, align=center},
  thickarrow/.style={->, >=Stealth, line width=1.2pt},
]
% Nodes
\node[box] (DIdiag) {DI${}_{diag}$};
\node[box, right=of DIdiag] (DIproj) {DI${}_{proj}$};
\node[box, right=of DIproj] (DIl) {DI${}_{l}$};
\node[box, right=of DIl] (DIi) {DI${}_{i}$};
\node[box, right=of DIi] (DI) {DI};
\node[box, above=of DIproj] (DIimm) {DI${}_{imm}$};
\node[box, below=of DIproj] (DIaut) {DI${}_{aut}$};
% Arrows
\draw[thickarrow] (DIdiag) -- (DIproj);
\draw[thickarrow] (DIproj) -- (DIl);
\draw[thickarrow] (DIl) -- (DIi);
\draw[thickarrow] (DIi) -- (DI);
\draw[thickarrow] (DIimm) -- (DIl);
\draw[thickarrow] (DIaut) -- (DIl);
\end{tikzpicture}
\caption{Strategy of proof of Theorem \ref{theo:DI}.}
\label{fig:di-properties}
\end{figure}

We begin with the case of linear maps in $\GL_n(O_K)$.

\begin{lemma}[DI${}_{aut}$]
Let $f \in GL_n(O_K)$ and $\PP$ a polyhedron in $K^n$.
Then $f(\PP)$ is a polyhedron. \label{lem:DIaut}
If in addition, $\PP$ is defined only by inequalities,
then so is $f(\PP)$.
\end{lemma}
\begin{proof}
If $\PP$ is defined (in matrix form) by \[\left\lbrace X \in K^n,  AX+B \geq 0, CX+D=0 \right\rbrace\] and $U$ is the matrix of $f$ in the canonical basis of $K^n$, 
let $\Qc$ be defined by \[\left\lbrace Y \in K^n,  AU^{-1} Y+B \geq 0, CU^{-1} Y+D=0 \right\rbrace.\]
Then it is clear that $\Qc$ is a polyhedron and $f(\PP)=\Qc.$
It is also clear that if $\PP$ is defined only by inequalities,
then so is $f(\PP)$.
\end{proof}

@@

\begin{lemma}[DI${}_{diag}$]
Let $f : K^n \to K^n$ be a linear map and $\PP$ a polyhedron in $K^n$ defined only by inequalities. We assume that the matrix of $f$ in the canonical basis of $K^n$ is diagonal.
Then $f(\PP)$ is a polyhedron. \label{lem:DIdiag}
\end{lemma}
\begin{proof}
As in the proof of Lemma \ref{lem:DIaut} DI${}_{aut}$, a trivial change
of variables is enough to conclude.
\end{proof}

@@

\begin{lemma}[DI${}_{proj}$]
Let $f : K^n \to K^n, \: (x_1,\dots,x_{n-1},x_n) \mapsto (x_1,\dots,x_{n-1})$ and $\PP$ a polyhedron in $K^n$ defined only by inequalities. 
Then $f(\PP)$ is a polyhedron defined only by inequalities. \label{lem:DIproj}
\end{lemma}
\begin{proof}
We assume that $\PP \neq \emptyset$.
Let us write the conditions defining $\PP$
in matrix form:
$\val(A X+B) \geq 0$ 
with $A \in M_{q,n}(K)$, $B \in K^q$
and $X=(x_1,\dots,x_n)^\intercal$.

@@

\begin{lemma}[DI${}_{imm}$]
  Let $f : K^l \to K^n$ be the immersion $(x_1,\dots, x_l) \mapsto (x_1,\dots, x_l,0,\dots, 0)$ and $\PP$
  a polyhedron in $K^l$. Then $f(\PP)$ is a polyhedron. \label{lem:DIimm}
\end{lemma}
\begin{proof}
Adding the equalities $x_{l+1}=0, \dots, x_n=0$ to the equations and inequations in
$x_1,\dots, x_l$ defining $\PP$, the result is clear.
\end{proof}

@@

\begin{proposition}[DI${}_l$]
Let $f : K^n \to K^m$ be a linear map and $\PP$ a polyhedron in $K^n$ defined only by inequalities.
Then $f(\PP)$ is a polyhedron. \label{prop:DIl}
\end{proposition}
\begin{proof}
We assume that $\PP \neq \emptyset$, and we identify $f$ with its matrix in $\allmat_{n,m}(K)$.
We assume that $\PP$ is defined as $\left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I\right\rbrace$ for some
finite sets $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I$ .

@@

We can generalize from linear mappings to affine mappings.
\begin{proposition}[DI${}_i$]
Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron in $K^n$ defined only by inequalities.
Then $f(\PP)$ is a polyhedron. \label{prop:DIi}
\end{proposition}
\begin{proof}
Let $P \in K^m$. One can see by immediate change of variables that $\Qc$ is a polyhedron in $K^m$ if and only if
$\Qc+P$ is a polyhedron in $K^m$.
Consequently, translating by $-f(O)$ in the codomain, one can reduce
to the case of Proposition \ref{prop:DIl}   DI${}_l$.
\end{proof}

@@

\begin{proof}[Proof of Theorem \ref{theo:DI} DI]
Here, $f : K^n \to K^m$ is an affine map and $\PP$ a polyhedron in $K^n.$
Let us write $\PP = \PP_I \cap \PP_E$
with $\PP_I := \left\lbrace X \in K^n,  AX+B \geq 0 \right\rbrace$
and $\PP_E := \left\lbrace X \in K^n,  CX+D=0 \right\rbrace = P + \overrightarrow{\PP_E}.$ 
Then $f(\PP) = f_{\PP_E}(\PP_I).$

By a translation of $-P$ in $K^n$, we can assume that
$\PP_E$ is a linear vector space: we are reduced to proving that, if $\tilde{f}: \PP_E \to K^m$ is an affine map and $\PP_I$ is a polyhedron in the vector space $\PP_E$ defined only by inequalities, then  $\tilde{f}(\PP_I)$ is a polyhedron.
This is the case thanks to Proposition \ref{prop:DIi} DI$_i$
and the theorem is proven.
\end{proof}

@@

\begin{proposition}[Characterization of polyhedra] \label{prop:carac}
    Non-empty polyhedra are image of polydiscs under a linear mapping.
\end{proposition}
\begin{proof}
    Let $\PP$ be a polyhedron in $K^n$. Then $\PP = \{x \in K^n : Ax+B \ge 0, Dx = e\}$ for some $A \in K^{d \times n}, b \in K ^d,  D\in  K^{m\times n}, e \in K^m$.

    If $\PP$ is nonempty then there exists $x_0 \in K^n$ such that $Dx_0=e$. Let $J \in K^{n \times R}$ such that $\textrm{Im} J = \ker D$ where $R$ denotes the dimension of $\ker D$. Then $\PP = x_0 + J\PP'$ where $A' := AJ$ $b' := Ax_0 + b$ and
    $\PP' := \{y \in K ^R: A'y + b' \ge 0 \}$.

    Now let $S \in K^{n\times R}$ be the SNF of $A'$ and $Q \in \GL_n\left(\mathcal{O}_K\right)$ and $P \in \GL_R\left(\mathcal{O}_K\right)$ such that $A'= Q S P^{-1}$.
    Then $\PP' = \{y \in K^R : QSP^{-1}y + b' \ge  0\} = P\{z \in K^R : Sz + Q^{-1}b' \ge 0 \}$.
    Let $b'':=Q^{-1}b$ then $P' = P \{z \in K^R : s_i z_i + b''_i \ge 0, i= 1\ldots R\}$. The set $\{z \in K^R : s_i z_i + b_i \ge 0\}$ is either empty or a polydisc (possibly with infinite radii) and $\PP = x_0 + JP \{z \in K^R: s_i z_i + b_i \ge  0, i=1,\ldots,R\}$ which concludes the proof.

@@

\begin{corollary} \label{cor:caracdim1}
   If $\PP$ is a polyhedron in $K$ then $\PP$ is either empty or a ball (possibly with infinite radius).
\end{corollary}

\begin{proof}
    Let $\PP$ be such polyhedron. We assume that $\PP \neq \emptyset$. By \ref{prop:carac} there exist a polydisc $D = \{x \in K^n : \val s_i x_i - b_i \ge 0, i=1,\ldots,n \}$ for some $s_1,\ldots,s_n, b_1,\ldots,b_n \in K ^n$ and an affine map $f : K^n \to K$ such that $\PP = f(D)$. Let $a_0,a_1,\ldots,a_n \in K$ such that $f(x) = a_0 + a_1 x_1 + \ldots + a_n x_n$. We can assume, with no loss of generality, that the $a_i$'s are nonzero.

If there exists $i_0 \in \{1,\ldots,n\}$ such that $s_{i_0} = 0$ then $\PP = f(D) = K$ and $\PP$ is a ball of infinite radius. Otherwise, we have $D = \{x \in K^n : x_i = \frac{b_i}{s_i} + O\left( \pi^{-val s_i} \right), i=1,\ldots,n \}$ and therefore for all $x \in  K$, $x \in P$ if and only if $x = a_0 + \sum_{i=1}^{n}( \frac{a_i b_i}{s_i} + O\left( \pi^{\val a_i - \val s_i} \right))= a_0  + \sum_{i=1}^{n} \frac{a_i b_i}{s_i} + O(\pi^d)$ where $d = \min \limits_{i = 1,\ldots,n} \val a_i - \val s_i$. Thus $\PP = \{x \in K : \val (x - a_0 - \sum_{i=1}^{n} \frac{a_i b_i}{s_i}) \ge d \}$ is a ball.

@@

A \emph{linear programming problem} (or \emph{linear program}) \emph{with data $(A,b,c,D,e)$} is defined
as:
\begin{equation}
  \tag{LP}\label{LP}
\begin{array}{rcll}
  p^* & := & \inf_{x \in K^n} & \val \left\langle c, x \right\rangle \\
  &    & \text{s.t.}         & A x + b \geq 0\\
  & & & D x = e
\end{array}
\end{equation}
with $c \in K^n$ a fixed vector of size $n$ that represents the cost,
$A \in K^{d \times n}$, $b \in K^d$, $D \in K^{m\times n}$, $e \in K^m$ 
and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$.
When $A$ is a diagonal matrix,
we refer to \eqref{LP} as a \emph{diagonal} linear program.
We denote the \emph{feasible set} of \eqref{LP} by
\begin{equation*}
\begin{aligned}
  \PP  &= \{x \in K^n : Ax + b \geq 0, Dx = e\}.
\end{aligned}
\end{equation*}
Note that $\PP$ is a polyhedron.
A vector $x \in K^n$ is called \emph{feasible} for~\eqref{LP} if $x \in \PP$. A feasible vector $x^* \in \PP$ is called a \emph{solution} to \eqref{LP} if $p^* = \val\left\langle c,x^*\right\rangle$, namely, if the infimum in \eqref{LP} is attained at $x^*$.

@@

\begin{lemma}\label{solutions}
  Let $(S,b',c',{\bf 0}, 0)$ be as in \Cref{solsLP} and assume \eqref{LP} is feasible.
  %%%$\PP' \neq \emptyset$.
  %%%= \{y \in K^n : Sy+b' \geq 0\}
  For $\lambda = -\sum_{i=1}^r c'_i b'_i/s_i$ and $v = \min_{1\le i\le r} \val (c'_i/s_i)$,
  one has:
  \begin{enumerate}
  \item
    if $\val \lambda < v$, the minimum is $\val \lambda$ and is attained on the whole feasible
    set; \label{solutions:it1}
  \item
    if $\val \lambda \geq v$, the minimum is $v$ and is attained on
    ${\bf e}_j \in K^n$, the vector with all $0$'s except with a $1$ on the $j$-th component,
    with $j$ satisfying $\val (c'_j/s_j) = v$. \label{solutions:it2}
  \end{enumerate}
  %One has
  %$$
  %\langle c',\PP'\rangle = \lambda + \pi^v\OK.
  %$$
  %If attained on every $x \in \PP'$;
\end{lemma}
\begin{proof}
  The feasible set $\PP' = \{y \in K^n : Sy+b' \geq 0\}$ of the diagonal LP can be written
  as the set of vectors $y \in K^n$ that verifies $s_i y_i + b'_i \in \OK$ for $i=1,...,r$.
  In other words:
  $$
  \PP' = \left\{\left[\begin{smallmatrix} y_1\\ \vdots\\ y_n \end{smallmatrix}\right] \in K^n :
  y_i \in -\frac{b'_i}{s_i} + \frac{1}{s_i} \OK, 1\le i\le r\right\}.
  $$
  The minimum in \eqref{LP} is the minimum of
  $y \mapsto \val\left(\left\langle c',y \right\rangle\right)$ on $\PP'$.
  The image of $\PP'$ by $y \mapsto \left\langle c',y \right\rangle$ is
  \[
  \left\langle c',\PP' \right\rangle = \sum_{i=1}^r -c'_i \frac{b'_i}{s_i} + \sum_{i=1}^r\left( \frac{c'_i}{s_{i}} \OK \right) = \lambda + \pi^{v} \OK.
  \]
  Two cases can occur depending on $v$ and the valuation of $\lambda$.
  If $\val(\lambda) < v$, the minimum of $y\mapsto \val\left(\left\langle c',y \right\rangle\right)$ over $\PP'$ is reached at any point of $\PP'$, and is equal to $\val(\lambda)$.
  Otherwise, $\lambda \in \pi^{v} \OK$ and the minimum is $v$ and is reached at any points $y$ of $\PP'$ such that
  $\left<c',y \right> \in \pi^v\OK$.
\end{proof}

@@

Recall that the \emph{Newton polygon} of a polynomial $P = \sum_{i=0}^{d} a_i T^i \in K[T]$ is
defined as the inferior convex hull of the set $\{(i, \val a_i) \,|\, 0 \le i \le d\}$, {\it i.e.} the
graph of the greatest convex function $\PP : [0,d] \to \R$ such that $\PP(i) \leq \val a_i$
for $i=1,\ldots,d$. This function is piecewise affine and its slopes are exactly the opposites of the valuations
of the roots of $P$.

@@

\begin{definition}
  A subset $S$ of $K^n$ is said \emph{semialgebraic} if it is defined by finite unions and intersections
  of sets defined by equalities of the form $\{x \in K^n  : p(x) = 0\}$
  and of sets defined by inequalities of the form $\{ x\in K^n : \val p(x) \geq 0\}$, for polynomials
  $p \in K[x]$.
\end{definition}
